Verifying Demonstrations

### 2018-02-25 paper/BuildingBlocks.tex
Changes order: distance bounding before anon creds
Writes about our needed hash functions

\dots

\input{anon-cred.tex}
\input{DistanceBounding.tex}
\input{LocationProofs.tex}
\input{TimeStamp.tex}

>>>>

We need a few primitives with special properties to build our protocol.

\subsection{Collision-resistant hash functions}

\NewAlgorithm{\Hash}{H}
\NewAlgorithm{\algA}{A}

One primitive that we need is a collision-resistant hash function, \Hash.

\begin{definition}[Collision resistance]
  Let \(\lambda\) denote the security parameter.
  We say that a hash function, \(\Hash\), is collision resistant if for any 
  \ac{PPT} algorithm \(\algA\) we have that
  \begin{multline*}
    \Pr\left[ x_1, x_2\gets \algA[1^\lambda] :
      \right. \\ \left.
      \Hash[x_1] = \Hash[x_2] \land x_1\neq x_2 \right] < \negl[\lambda].
  \end{multline*}
\end{definition}

Thus we can instantiate \(\Hash\) with any algorithm from the SHA-2 or SHA-3 
families.

\input{DistanceBounding.tex}
\input{anon-cred.tex}
\input{LocationProofs.tex}
\input{TimeStamp.tex}
